\documentclass[letter,12pt]{article}

\include{cv-commands}

\begin{document}

\header
{Kristi Short}
{kshort@iastate.edu}
{136-E University Village\\
Ames, IA\\
(941) 830-0690}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{statementblock}{}
To obtain a part time position working in an area involving topics relevant to my mathematics background. 
\smallskip
\end{statementblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Education}

\resumeitem{Bachelor of Science}{{Mathematics}, November 2015 - \href{http://sfcollege.edu{Santa Fe College}}

\resumeitem{Bachelors of Science}{{Pure Mathematics}, August 2012 - 2014}
\href{http://mills.edu{Mills College}}
\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Skills}
 
\resumeitem{Ninja}{Kicking\experiencemost, screaming\experiencemid, running away\experiencemost, furtive glances\experiencelow, funny outfits\experiencemid}

\resumeitem{Embroidery}{Laser embroidery\experiencemost, needles\experiencemid, thread\experiencelow, puppies\experiencemid, horsies\experiencelow}

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Jobs}

\resumeitem{January 2012 -\\Present}{MegaCorp, Inc - Virtual janitorial assistant manager. Discrete removal of indiscreet items.}

\resumeitem{January 2011 -\\December~2011}{Self employed - President/CEO. Hiring and firing. Mergers and acquisitions. Profiteering and philanthropic mentoring.}

\resumeitem{January 1903 -\\December~2010}{Vague - Unknown. Duties as described. Mandatory ad hoc committee attendance bi-monthly.}

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{pubblock}{Talks and Publications}

\pubitemx{An explanation of everything (revised)}{, \textbf{J. McDoe}, H. Smiths; 2013}

\pubitema{A generalized method of finding one's feet in a category 9 blizzard}{, S. Claus \textbf{J. McDoe}, D. Marr; Podiatric Weather Journal Vol. 24, No. 5, p. 74, July 2012}

\pubitemi{What the hell?}{, The living room, midnight, Jan. 2012}

\pubitemp{How to bribe conference officials and other tips and tricks}{, Anonymous, \textbf{J. McDoe} (as ghost author); Conferences 2011! Vol. 761, No. 89, p. 15455, Nov. 2011}

\pubitemt{Please, get off my lawn.}{, The Whitehouse, Washington, DC, Feb. 2011}

\pubitemj{Mold I found under my fridge last week}{, \textbf{J. McDoe}; Nature Vol. 89, No. 3, p. 3, Mar. 2010}

\end{pubblock}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblockb}{Activities}

\item {Competitive lawn dart association referee of the year runner-up. 2004}
\item {Tai Chi for pets}
\item {Resume templating in \LaTeX}

\end{resumeblockb}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}
