\documentclass[13pt]{article}

\usepackage{punk}
\usepackage[T1]{fontenc}

\begin{document}
\pagestyle{empty}
\section*{Rules for Getting Along with Kristi}

\begin{enumerate}
\item \textbf{No Politics until at least my THIRD cup of coffee.} If you don't know which cup I'm on error on the side of less than three. \emph{If you're claiming a constitutional argument you better know what the Constitution (US) actually says (because I do).} Fuck that, NO POLITICS.
\item If you want to debate something be prepared to be objective and not take arguments as personal attacks, especially if you identify with your argument (an ill-advised practice).
\item It would be a good idea to know when you've made an assumption and what exactly those assumptions are.
\item I do NOT Care if you think \emph{``Its stupid/boring/dumb''} or if you \emph{``dont want to''}, that goes for whatever \emph{``IT''} is. You're going to do it now or later after you've wasted YOUR time sitting there not doing anything to figure you'd better.
\item If it doesn't need to be done RIGHT now, ask me now but you should definitely remind me close to the time it needs to be done.
\item Have I had coffee? If answer is no. Don't. 
\item Dont ask for advice when you just want validation.
\item Dont ask questions you dont want answers to.
\item Dont ask questions just to ask questions.
\item \textbf{READ THE INSTRUCTIONS}
\item Think first, then do it again.
\item The milk is in the fridge.
\item \textbf{Dont interrupt the focus timer!!! I have ADD Remember! Because I frequently dont and apparently love distractions and that is a VERY BAD thing!}
\item Dont yell my name down the hall unless its actually an emergency (something better be dead or dying), if its actually important you will come ask me.
\end{enumerate}
\end{document}